?????????????????

### 2022-12-01 article_1/Result1.tex
Change results (tables and figures) and update apsg library

\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but with different directions), according to \cref{tab:ModelTab}. Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a grid spacing of 1 μm. Subsequently, the data vector was contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and 25 nT standard deviation, as shown in \cref{fig:SimpleSynthetic}a.}

@@

\floatsetup[table]{capposition=top} % to put the caption on the top of the table
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\input{input_par_table}

@@

\noindent{After isolante the potencial field data and first derivatives for each source, we can solve the 3D Euler deconvolution \cref{eq:euler2} proposed by  \cite{Reid1990}, one for each subarea selected (window data), by assuming the structural index of a sphere/punctual source (N = 3). Thus, obtaining a sturdy result for the central positioning (Xc, Yc, Zc) of each source causing the magnetic potential anomaly in the observed data set, as shown in \cref{tab:InversionTab}.}

\noindent{The last step consists of using the central positions of each source, obtained with Euler's method, as an input parameter for inverting the original noisy data (\cref{fig:SimpleSynthetic}a) to find the least squares (or robust) approximation solution for the vector of cartesian magnetic moments ($\bar{m}$). With this, the magnetization directions (D and I) and the intensity of the magnetic moment can be estimated using equations (\cref{eq:sphere16,eq:sphere17,eq:sphere17_m}), as well as the uncertainty propagation of this inversion, using equations (\cref{eq:sphere21,eq:sphere22,eq:sphere22_m}) and considering $\sigma$ = 25nT. The results obtained with the least squares estimator can also be seen in \cref{tab:InversionTab}.}

% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\input{solution_par_table}

@@

>>>>

\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but with different directions), according to \cref{tab:SimpleSyntheic}. Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a grid spacing of 1 μm. Subsequently, the data vector was contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and 15 nT standard deviation, as shown in \cref{fig:SimpleSynthetic}a.}

@@

\floatsetup[table]{capposition=top} % to put the caption on the top of the table
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\input{simple_synthetic_table}

@@

\noindent{After isolante the potencial field data and first derivatives for each source, we can solve the 3D Euler deconvolution \cref{eq:euler2} proposed by  \cite{Reid1990}, one for each subarea selected (window data), by assuming the structural index of a sphere/punctual source ($n = 3$). Thus, obtaining a sturdy result for the central positioning (Xc, Yc, Zc) of each source causing the magnetic potential anomaly in the observed data set, as shown in \cref{tab:InversionTab}.}

\noindent{The last step consists of using the central positions of each source, obtained with Euler's method, as an input parameter for inverting the original noisy data (\cref{fig:SimpleSynthetic}a) to find the least squares (or robust) approximation solution for the vector of cartesian magnetic moments ($\bar{m}$). With this, the magnetization directions (D and I) and the intensity of the magnetic moment can be estimated using equations (\cref{eq:sphere16,eq:sphere17,eq:sphere17_m}), as well as the uncertainty propagation of this inversion, using equations (\cref{eq:sphere21,eq:sphere22,eq:sphere22_m}) and considering $\sigma$ = 25nT. The results obtained with the least squares estimator can also be seen in \cref{tab:SimpleSyntheic}.}

@@

\begin{figure}[hbpt]
\centering
\includegraphics[width=1.0\textwidth]{ComplexComparison.png}
\caption{blablabla.}
\label{fig:ComplexSynthetic2}
\end{figure}

\begin{figure}[hbpt]
\centering
\includegraphics[width=1.0\textwidth]{ComplexStereo.png}
\caption{blablabla.}
\label{fig:ComplexSynthetic3}
\end{figure}
